---
title: "IPL Dataset analysis with R"
author: "K.V.Yaswanth"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

###IPL DTA SET ANALYIS WITH R PROGRAMMING USING DPLYR PACKAGE###
#### Objective- To analyze the IPL matches and deliveries datasets and obtain inferences.


#Loading required packages

```{r}
library(dplyr)
```

#Read data sets

```{r}
matches_data<-read.csv("C:/Users/Yaswanth Karri/Desktop/matches.csv")
deliveries_data <- read.csv("C:/Users/Yaswanth Karri/Desktop/deliveries.csv/deliveries.csv")
```

#Integrating both datasets

```{r}
data <- bind_rows(matches_data,deliveries_data)
```

#Data Cleaning

```{r}
data<- select(data, -c(umpire1,umpire2))
```

#Knowing the data

```{r}
head(matches_data)
head(deliveries_data)
str(matches_data)
str(deliveries_data)
```

#Total number of matches in the dataset

```{r}
length(data$id) 
```

#Total number of seasons 

```{r}
length(unique(data$season))
```

#Total number of matches played in each season

```{r}
data %>% 
  group_by(season) %>%
  dplyr::summarize(number_of_matches = n())%>% arrange(desc(number_of_matches))
```

#Number of matches played at a particular venue in descending order

```{r}
data%>% 
  group_by(venue) %>%
  dplyr::summarize(nmatches = n())%>%arrange(desc(nmatches))
```

#IPL teams and their number of wins in descending order

```{r}
data %>% 
  group_by(winner) %>%
  dplyr::summarize(wins = n())%>% arrange(desc(wins))

```
#Teams dominating in certain locations

```{r}
data%>% 
  filter(result != 'no result') %>% group_by(winner,city) %>% 
  dplyr::summarise(win = n()) %>% arrange(desc(win))
```

#Teams which were not able to perform well in non-home location

```{r}
data%>% 
  filter(result != 'no result') %>% group_by(winner,city) %>% 
  dplyr::summarise(win = n()) %>% arrange((win))
```

#Best IPL batsmen

```{r}
data%>% 
  group_by(batsman) %>% 
  dplyr::summarise(runs =length(batsman_runs)) %>% arrange(desc(runs))
```

#Best IPL bowlers

```{r}
data %>% group_by(bowler) %>% filter(player_dismissed!="") %>% 
  dplyr::summarise(wickets= n())%>% arrange(desc(wickets)) 

```

#Most Man of the match awards

```{r}
matches_data %>% 
  group_by(player_of_match) %>%
  dplyr::summarize(awards = n())%>% arrange(desc(awards))

```


